Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists

### 2024-03-01 paper.Rmd
minor edits

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(forcats)
# read data
pre_surveys <- readRDS("data/pre_workshop_surveys.rds")
post_surveys <- readRDS("data/post_workshop_surveys.rds")
# factore levels for charts
factor_levels <- c("Excellent", "Good", "Sufficient", "Insufficient", "Not shared")

@@

```{r, computer-skills, fig.cap="The computer skills of the respondents.", out.width="50%"}
pre_surveys %>%
  select(`Which.computer.skills.do.you.have....Selected.Choice`) %>%
  separate_rows(`Which.computer.skills.do.you.have....Selected.Choice`, sep = ',\\s*') %>%
  filter(`Which.computer.skills.do.you.have....Selected.Choice`!="") %>%
  group_by(`Which.computer.skills.do.you.have....Selected.Choice`) %>%
  ggplot(aes(x=`Which.computer.skills.do.you.have....Selected.Choice`)) + geom_bar() +
    xlab("Computer skills") + coord_flip()
```

```{r, abm-knowledge, fig.cap="Respondents knowledge and experience with ABM.", fig.show="hold", out.width="50%"}
pre_surveys %>% 
  filter(`Do.you.know.what.Agent.Based.Modeling.is.`!="Not shared") %>% 
  ggplot(aes(x = `Do.you.know.what.Agent.Based.Modeling.is.`)) +
    geom_bar(na.rm = TRUE) + xlab("I know what ABM is") + facet_grid(~Workshop)
pre_surveys %>%
  select(`Which.software.do.you.know.for.Agent.Based.Modeling....Selected.Choice`) %>%
  filter(`Which.software.do.you.know.for.Agent.Based.Modeling....Selected.Choice`!="") %>%
  separate_rows(Which.software.do.you.know.for.Agent.Based.Modeling....Selected.Choice, sep = ',\\s*') %>%
  group_by(`Which.software.do.you.know.for.Agent.Based.Modeling....Selected.Choice`) %>%
  ggplot(aes(x=`Which.software.do.you.know.for.Agent.Based.Modeling....Selected.Choice`)) + geom_bar() +
  xlab("ABM Software known") + coord_flip()
```

@@

```{r, available-theory, fig.cap="Respondents optionion on the quality of theory on ABM faceted out by event.", fig.width=11}
pre_surveys %>%
  select(`How.do.you.judge.the.available.theory.on.Agent.Based.Modelling.`, Workshop) %>%
  filter(`How.do.you.judge.the.available.theory.on.Agent.Based.Modelling.`!="") %>%
  mutate(`How.do.you.judge.the.available.theory.on.Agent.Based.Modelling.` =
           fct_relevel(`How.do.you.judge.the.available.theory.on.Agent.Based.Modelling.`,
                       "No opinion", "Limited", "Sufficient", "More than sufficient", "Very good")) %>%
  ggplot(aes(x = `How.do.you.judge.the.available.theory.on.Agent.Based.Modelling.`)) +
  geom_bar() + xlab("Quality of theory on ABM") + coord_flip() +
  facet_grid(~Workshop)
```

@@

```{r, rating-workshop, fig.cap="Respondents rating of the workshop in general faceted for each event.", fig.width=11}
post_surveys %>%
  mutate(How.would.you.rate.the.workshop.in.general. = fct_relevel(How.would.you.rate.the.workshop.in.general., factor_levels)) %>%
  ggplot(aes(x=How.would.you.rate.the.workshop.in.general.)) + geom_bar() +
  xlab("Rating of the workshop") + facet_grid(~Workshop) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

```{r, rating-teaching, fig.cap="Respondents rating of the teaching material in general faceted for each event.", fig.width=11, fig.show='hold', out.height="50%"}
post_surveys %>%
  mutate(How.would.you.rate.the.teaching.material. = fct_relevel(How.would.you.rate.the.teaching.material., factor_levels)) %>%
  ggplot(aes(x=How.would.you.rate.the.teaching.material.)) + geom_bar() +
  xlab("Rating of the teaching material") + facet_grid(~Workshop) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
post_surveys %>%
  mutate(How.would.you.rate.the.trainers.teachers. = fct_relevel(How.would.you.rate.the.trainers.teachers., factor_levels)) %>%
  ggplot(aes(x=How.would.you.rate.the.trainers.teachers.)) + geom_bar() +
  xlab("Rating of the teacher") + facet_grid(~Workshop) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

```{r, future-abm, fig.cap="The respondents reaction to the question if they thing that they will apply ABM in the future."}
post_surveys %>%
  filter(!is.na(Do.you.think.that.you.will.apply.ABM.to.your.own.research..If.yes..can.you.elaborate....Selected.Choice)) %>%
  ggplot(aes(x = 1, fill = `Do.you.think.that.you.will.apply.ABM.to.your.own.research..If.yes..can.you.elaborate....Selected.Choice`)) +
  geom_bar(na.rm = TRUE) + coord_polar(theta = "y", start=0) + theme_void() +
  scale_fill_discrete(name = paste0("Will apply ABM in the future (n=", sum(!is.na(post_surveys$Do.you.think.that.you.will.apply.ABM.to.your.own.research..If.yes..can.you.elaborate....Selected.Choice)), ")"),
                      labels = c("No", "Yes"))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(forcats)
# read data
pre_surveys <- readRDS("data/pre_workshop_surveys.rds")
post_surveys <- readRDS("data/post_workshop_surveys.rds")
# factore levels for charts
factor_levels <- c("Excellent", "Good", "Sufficient", "Insufficient", "Not shared")

@@

```{r, computer-skills, fig.cap="The computer skills of the respondents.", out.width="50%", echo=FALSE}
pre_surveys %>%
  select(`Which.computer.skills.do.you.have....Selected.Choice`) %>%
  separate_rows(`Which.computer.skills.do.you.have....Selected.Choice`, sep = ',\\s*') %>%
  filter(`Which.computer.skills.do.you.have....Selected.Choice`!="") %>%
  group_by(`Which.computer.skills.do.you.have....Selected.Choice`) %>%
  ggplot(aes(x=`Which.computer.skills.do.you.have....Selected.Choice`)) + geom_bar() +
    xlab("Computer skills") + coord_flip()
```

```{r, abm-knowledge, fig.cap="Respondents knowledge and experience with ABM.", fig.show="hold", out.width="50%", echo=FALSE}
pre_surveys %>% 
  filter(`Do.you.know.what.Agent.Based.Modeling.is.`!="Not shared") %>% 
  ggplot(aes(x = `Do.you.know.what.Agent.Based.Modeling.is.`)) +
    geom_bar(na.rm = TRUE) + xlab("I know what ABM is") + facet_grid(~Workshop)
pre_surveys %>%
  select(`Which.software.do.you.know.for.Agent.Based.Modeling....Selected.Choice`) %>%
  filter(`Which.software.do.you.know.for.Agent.Based.Modeling....Selected.Choice`!="") %>%
  separate_rows(Which.software.do.you.know.for.Agent.Based.Modeling....Selected.Choice, sep = ',\\s*') %>%
  group_by(`Which.software.do.you.know.for.Agent.Based.Modeling....Selected.Choice`) %>%
  ggplot(aes(x=`Which.software.do.you.know.for.Agent.Based.Modeling....Selected.Choice`)) + geom_bar() +
  xlab("ABM Software known") + coord_flip()
```

@@

```{r, available-theory, fig.cap="Respondents optionion on the quality of theory on ABM faceted out by event.", fig.width=11, echo=FALSE}
pre_surveys %>%
  select(`How.do.you.judge.the.available.theory.on.Agent.Based.Modelling.`, Workshop) %>%
  filter(`How.do.you.judge.the.available.theory.on.Agent.Based.Modelling.`!="") %>%
  mutate(`How.do.you.judge.the.available.theory.on.Agent.Based.Modelling.` =
           fct_relevel(`How.do.you.judge.the.available.theory.on.Agent.Based.Modelling.`,
                       "No opinion", "Limited", "Sufficient", "More than sufficient", "Very good")) %>%
  ggplot(aes(x = `How.do.you.judge.the.available.theory.on.Agent.Based.Modelling.`)) +
  geom_bar() + xlab("Quality of theory on ABM") + coord_flip() +
  facet_grid(~Workshop)
```

@@

```{r, rating-workshop, fig.cap="Respondents rating of the workshop in general faceted for each event.", fig.width=11, echo=FALSE}
post_surveys %>%
  mutate(How.would.you.rate.the.workshop.in.general. = fct_relevel(How.would.you.rate.the.workshop.in.general., factor_levels)) %>%
  ggplot(aes(x=How.would.you.rate.the.workshop.in.general.)) + geom_bar() +
  xlab("Rating of the workshop") + facet_grid(~Workshop) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

```{r, rating-teaching, fig.cap="Respondents rating of the teaching material in general faceted for each event.", fig.width=11, fig.show='hold', out.height="50%", echo=FALSE}
post_surveys %>%
  mutate(How.would.you.rate.the.teaching.material. = fct_relevel(How.would.you.rate.the.teaching.material., factor_levels)) %>%
  ggplot(aes(x=How.would.you.rate.the.teaching.material.)) + geom_bar() +
  xlab("Rating of the teaching material") + facet_grid(~Workshop) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
post_surveys %>%
  mutate(How.would.you.rate.the.trainers.teachers. = fct_relevel(How.would.you.rate.the.trainers.teachers., factor_levels)) %>%
  ggplot(aes(x=How.would.you.rate.the.trainers.teachers.)) + geom_bar() +
  xlab("Rating of the teacher") + facet_grid(~Workshop) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

```{r, future-abm, fig.cap="The respondents reaction to the question if they thing that they will apply ABM in the future.", out.height="50%", echo=FALSE}
post_surveys %>%
  filter(!is.na(Do.you.think.that.you.will.apply.ABM.to.your.own.research..If.yes..can.you.elaborate....Selected.Choice)) %>%
  ggplot(aes(x = 1, fill = `Do.you.think.that.you.will.apply.ABM.to.your.own.research..If.yes..can.you.elaborate....Selected.Choice`)) +
  geom_bar(na.rm = TRUE) + coord_polar(theta = "y", start=0) + theme_void() +
  scale_fill_discrete(name = paste0("Will apply ABM in the future (n=", sum(!is.na(post_surveys$Do.you.think.that.you.will.apply.ABM.to.your.own.research..If.yes..can.you.elaborate....Selected.Choice)), ")"),
                      labels = c("No", "Yes"))
```

### 2024-03-01 paper.tex
minor edits

\begin{verbatim}
## Warning: There was 1 warning in `mutate()`.
## i In argument: `How.would.you.rate.the.workshop.in.general. =
##   fct_relevel(How.would.you.rate.the.workshop.in.general., factor_levels)`.
## Caused by warning:
## ! 1 unknown level in `f`: Not shared
\end{verbatim}

@@

\begin{verbatim}
## Warning: There was 1 warning in `mutate()`.
## i In argument: `How.would.you.rate.the.teaching.material. =
##   fct_relevel(How.would.you.rate.the.teaching.material., factor_levels)`.
## Caused by warning:
## ! 1 unknown level in `f`: Insufficient
\end{verbatim}

\begin{verbatim}
## Warning: There was 1 warning in `mutate()`.
## i In argument: `How.would.you.rate.the.trainers.teachers. =
##   fct_relevel(How.would.you.rate.the.trainers.teachers., factor_levels)`.
## Caused by warning:
## ! 1 unknown level in `f`: Insufficient
\end{verbatim}

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/future-abm-1.pdf}
\caption{\label{fig:future-abm}The respondents reaction to the question if they thing that they will apply ABM in the future.}
\end{figure}

>>>>

@@

@@

\begin{figure}
\includegraphics[height=0.5\textheight]{paper_files/figure-latex/future-abm-1} \caption{The respondents reaction to the question if they thing that they will apply ABM in the future.}\label{fig:future-abm}
\end{figure}
